\vspace{-1em}\thetitle

### 2009-08-14 paper.tex
...

When traffic traces are represented like this, a very curious thing happens:
the resulting matrices exhibit a great deal of linear structure.
Specifically, flow behaviors tend to lie near the union of a small set of low-rank subspaces.
\Figure{svd}~shows this structure visually.
The scatter plots show the first two most significant dimensions of the behavior matrix after reduction via singular value decomposition (\caps{SVD}) and projection onto the unit-sum hyperplane.

\begin{figure}[t]
\vspace{-0.9em}
\begin{center}
\subfloat[\scriptsize{DART.}]{\includegraphics[width=1.059in]{svd/dart}}
% \subfloat[\scriptsize{IETF 60}]{\includegraphics[width=1.059in]{svd/ie60}}
% \subfloat[\scriptsize{SIGCOMM 2004}]{\includegraphics[width=1.059in]{svd/sc04}}
\subfloat[\scriptsize{IETF 67}]{\includegraphics[width=1.059in]{svd/ie67}}
% \subfloat[\scriptsize{SIGCOMM 2001}]{\includegraphics[width=1.059in]{svd/sc01}}
\subfloat[\scriptsize{UCSD}]{\includegraphics[width=1.059in]{svd/ucsd}}
\caption{Scatter plots of the two most significant dimensions of the feature-frequency representations of traffic samples from the six network traffic traces considered in this paper.} 
\fig{svd}
\end{center}
\vspace{-2em}
\end{figure}

@@

>>>>

When traffic traces are represented like this, a very curious thing happens:
the resulting matrices exhibit a great deal of linear structure.
Specifically, flow behaviors tend to lie near the union of a small set of low-rank subspaces.
\Figure{svd}~shows this structure visually.
These scatter plots show the first two most significant dimensions of the behavior matrix after reduction via singular value decomposition (\caps{SVD}) and projection onto the unit-sum hyperplane.

\begin{figure}[t]
\vspace{-0.9em}
\begin{center}
\subfloat[\scriptsize{DART.}]{\includegraphics[width=1.059in]{svd/dart}}
% \subfloat[\scriptsize{IETF 60}]{\includegraphics[width=1.059in]{svd/ie60}}
% \subfloat[\scriptsize{SIGCOMM 2004}]{\includegraphics[width=1.059in]{svd/sc04}}
\subfloat[\scriptsize{IETF 67}]{\includegraphics[width=1.059in]{svd/ie67}}
% \subfloat[\scriptsize{SIGCOMM 2001}]{\includegraphics[width=1.059in]{svd/sc01}}
\subfloat[\scriptsize{UCSD}]{\includegraphics[width=1.059in]{svd/ucsd}}
\caption{Scatter plots of the two most significant dimensions of the feature-frequency representations of traffic samples from the six network traffic traces analyzed in our experiments.} 
\fig{svd}
\end{center}
\vspace{-2em}
\end{figure}

@@

For our experiments, we use randomly sampled traffic from six network traces.
The traces are freely available from the \caps{CRAWDAD} trace repository~\cite{Yeo06}.
Details of the traces are shown in \Table{traces}.
These data sets represent a broad cross-section of traffic patterns over time and a reasonable variety of network types.
% Unfortunately, we could not find any freely available residential or corporate network traces that were usable for our analysis.
We randomly sampled 5000 flows from each trace for training and another 5000 flows for testing.
Since the initial five packets are used for prediction, we consider only flows with at least five packets.
